\chapter{Conclusion}\label{chp:LABEL_CHP_5}

In this work, we demonstrated the versatility and expressiveness of the ray marching technique. Initially, we compared ray tracing and ray marching, highlighting their similarities and differences. Signed Distance Functions were also presented as a flexible mathematical representation of 
geometry, allowing us to easily apply techniques for the construction of procedural scenes. After building a strong foundation upon these concepts, we explored how this technique can be employed to render volumetric clouds in real time. We were effectively able to produce visually convincing results, while adopting an iterative approach that presented code snippets and algorithms supported by rendered examples, ultimately providing a comprehensive overview of ray marching and its capabilities.

\section{Future Works}

Although the presented methods provide a strong foundation for cloud rendering, further explorations could be made to apply more physically accurate shading on clouds. State of the art cloud rendering technology is built upon the presented foundation, and on top of that, Beer's Law & Powder Effect is applied in Horizon Zero Dawn's cloud rendering. % Adicionar Referências

Regarding Signed Distance Fields, many other applications are open: from Font Rendering, Ambient Sound the approximation of signed distance fields from mesh data using neural networks. 

Regarding Signed Distance Fields, many other applications are open: from font rendering 
\cite{green2007siggraph} and ambient sound propagation \cite{tiagocesar}, to the 
approximation of distance fields from mesh data using neural networks 
\cite{atzmon2019sal, park2019deepsdf}. Beyond these, SDFs have been employed in collision 
detection \cite{van2011sdfcollisions}, constructive solid geometry 
\cite{hart1996csgeometry}, and efficient pathfinding, due to their compact representation 
of spatial information. Recent research also investigates their role in differentiable 
rendering \cite{nimier2020differentiable} and implicit neural representations, where SDFs 
provide a continuous and differentiable description of geometry. These diverse 
applications highlight the versatility of SDFs as a unifying mathematical framework, 
bridging the gap between real-time graphics, physical simulation, and emerging machine 
learning methods.

% Beer's Law & Powder Effect https://progmdong.github.io/2019-03-04/Volumetric_Rendering/
% Mencionar outros metodos de obter formas complexas como:
% GRIDS: https://renderdiagrams.org/2017/12/28/signed-distance-fields/
% https://steamcdn-a.akamaihd.net/apps/valve/2007/SIGGRAPH2007_AlphaTestedMagnification.pdf
% NEURAL NETWORKS: 